\begin{longtable}{@{}p{0.24\linewidth}p{0.54\linewidth}p{0.14\linewidth}@{}}
\caption{PRISMA-ScR checklist crosswalk.}
\label{tab:prisma-checklist}\\
\toprule
Item & Reporting location & Status \\
\midrule
\endfirsthead
\toprule
Item & Reporting location & Status \\
\midrule
\endhead
Title and abstract & Title and structured abstract identify the manuscript as a scoping review and summarize source selection, charting, and synthesis. & Reported \\
Rationale & Introduction explains why heterogeneous breathing strategies require mapping before definitive efficacy recommendations. & Reported \\
Objectives & Introduction states mapping objectives for study characteristics, interventions, outcomes, feasibility, safety, and exploratory effects. & Reported \\
Eligibility criteria & Methods describe eligible breathing techniques, populations, and sport/performance contexts. & Reported \\
Information sources & Methods identify the databases, citation searching, and extraction dataset. & Reported \\
Selection of sources & Results include Figure~\ref{fig:prisma-flow}. & Reported \\
Data charting & Methods describe bibliometric, participant, intervention, outcome, feasibility, and safety fields. & Reported \\
Synthesis of results & Results combine descriptive mapping, plots, and exploratory effect synthesis. & Reported \\
Critical appraisal & Methods state that formal risk-of-bias appraisal was not the central scoping-review objective; reporting completeness is summarized instead. & Reported \\
Limitations & Discussion describes database/source-set, extraction, reporting, heterogeneity, and meta-analysis limitations. & Reported \\
Funding and conflicts & Declarations section included. & Reported \\
\bottomrule
\end{longtable}
